\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\begin{eg}[]
	Let $ L=10$cm,  $ k=1$ cm$ ^2$/sec (copper) and $ t=0.35$sec and use the first 8 terms.
	 \[
		 u(x,0.35) \approx \frac{400}{\pi} \sum_{ p= 1}^{ 8} \frac{1}{2p-1} e^{-[(2p-1) \frac{\pi}{10}]^2 0.35} \sin \left( \frac{(2p-1) \pi x}{10 } \right) 
	.\] 
	See lecture slide for graph.

	In this case, $ \overline{u}(x)=0$ and for each $ x$,
	 \[
		 u(x,t) \to 0 \text{ as } t \to \infty 
	.\] 
\begin{note}[]
	Recall $ \Phi = -K_0 \frac{\partial u}{\partial x} $. Consider the $ x$-term in  $ u_n(x,t)$
\begin{align*}
	\left[ \sin \left( \frac{ n\pi x}{ L} \right)  \right]' = n \cdot \frac{\pi}{L} \cos \left( \frac{ n\pi x}{ L} \right)  
\end{align*}
Thus the derivative wrt $ x$ is proportional to $ n$ and  $ \Phi$. That is, as $n $ increases, the derivative increases, and the heat flux (loss) increases. So the slowest decaying term is when $ n$ is smallest,  \emph{i.e.} $ n=1$. 
\end{note}

Establishing that the slowest decaying term (dominant term) is at $ n=1$ and for large  $ t$, we can use the  $ n=1$ term (called the "first Fourier mode") as an approximation
	 \[
		 u(x,t) \approx B_1 \sin \left( \frac{ \pi x}{ L} \right) e^{-( \frac{ \pi}{L} )^2 kt} 
	.\] 
	and we can use this for long term temperature prediction.
So for this problem we use the approximation:
\[
	u(x,t) \approx \frac{400}{\pi} \sin \left( \frac{ \pi x}{ L} \right) e^{-( \frac{ \pi}{L} )^2 kt} 
.\] 
to analyze the dynamics of the temperature when $ t $ grows. We expect $ u(x,t) \to 0 $ as $ t \to \infty$. See lecture slides for graph. 
\end{eg}

\begin{eg}[estimating cooling time]
How long will it take for the maximum absolute temperature of the rod to be less than $ \frac{1}{10}$ the initial maximum absolute temperature?

We wish to find $ t$  such that 
\[
	\max_{0<x<L} |u(x,t)| \leq \frac{1}{10} \max_{0<x<L} |f(x)|
.\]

Using the first Fourier mode approximation obtained above, recall there is an upper bound (in fact it's the least upper bound/supremum)
\[
	|u(x,t)| \leq \frac{400}{\pi} e^{-(\frac{\pi}{L})^2 kt}
.\] 
Hence this upper bound is greater or equal to the maximum (in this case they are in fact equal). Thus it suffices to find $ t$  such that 
\[
	\frac{400}{\pi} e^{-(\frac{\pi}{L})^2 kt} \leq \frac{1}{10} \cdot 100 = 10
.\] 
Solving this inequality yields
\[
	t \geq \frac{L^2}{k}\frac{1}{\pi^2} \ln \left( \frac{40}{\pi} \right) 
.\] 
\end{eg}


\newpage
\section{Insulated Rods}

Consider the following BVP:
\begin{equation*}
\begin{cases}
	\text{ PDE: }& \frac{\partial u}{\partial t} = k \frac{\partial^2 u}{\partial { x}^2},\qquad  0<x<L,t>0 \\
	\text{ BC: } & \frac{\partial u}{\partial x}(0,t)=0= \frac{\partial u}{\partial x} (L,t), \qquad  t>0\\
	\text{ IC: } & u(x,0) = f(x), \qquad  0 \leq x \leq L\\ 
\end{cases}
\end{equation*}

Recall Fourier's Law of Heat Conduction regarding the heat flux
\[
\Phi=-K_0 \frac{\partial u}{\partial x} 
.\] 
So here the BCs imply that there is no heat flow at the ends of the rod, \emph{i.e.} the rod is insulated on all sides.

Since there is no external source of heat, we expect this BVP to have a steady state solution.

Hence we can assume the solution has the form
\[
	u(x,t) = \overline{u}(x) + v(x,t)
.\] 

In fact, we can skip this decomposition step because the BVP already gives us a nice vector space due to the homogeneous BCs. And $ \lambda =0$ case will give us the steady-state solution anyway.


\end{document}
