\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\newpage
\section{Motion of a guitar string}

For a plucked guitar string at $ t=0$, the initial position, $ U(x)$, looks like either a sharp isosceles triangle or a hill-like smooth curve.

In either case  $ U(x)$ is continuous and  $ U'(x)$ is piecewise continuous or smooth. Note that if the initial velocity is  $ V(x)=0$ then  $ B_n=0$. If the initial position is given by
\begin{equation*}
	U(x)=
\begin{cases}
	\frac{ax}{h}, &0<x\leq h\\
	\frac{a(L-x)}{L-h }, & h<x<L\\
\end{cases}
\end{equation*}
Then using integration by parts, we get
\[
	A_n = \frac{2a \sin(n\pi h /L)}{(n\pi)^2 \frac{h}{L} \frac{L-h}{L }}
.\] 
We can guess this converges because of $ n^2$ term on the denominator.

So the position of the string is
\[
	u(x,t) = \sum_{ n= 1}^{\infty} \frac{2a}{\pi^2} \frac{L}{h} \frac{L}{L-h} \frac{\sin(n \pi h /L)  )}{n^2 } \cos \left( \frac{n\pi ct}{L } \right) \sin \left( \frac{ n\pi x}{ L} \right) 
.\]

I claim that this converges absolutely:
\[
	0\leq \sum_{ n= 1}^{\infty} | u(x,t)| \leq \sum_{ n= 1}^{\infty} \frac{M}{n^2}
\]
for some constant $ M>0$, so it converges absolutely. Hence it converges uniformly to a continuous function. But note
 \[
	 \frac{\partial^2 u}{\partial { x}^2} = \sum_{ n= 1}^{\infty} \frac{2a}{\pi^2} \frac{L}{h} \frac{L}{L-h} \frac{\sin(n \pi h /L)  )}{n^2 }  \cdot - \left( \frac{n \pi x}{L } \right) ^2 \cdot \cos \left( \frac{ n\pi c t}{ L} \right) \sin \left( \frac{ n\pi x}{ L} \right) 
.\] 
Notice $ n^2$ that helped achieving convergence got canceled! By divergence test (take n to infinity but the term doesn't go to zero), this doesn't converge. This is okay because in practice we always use a finite sum, so divergence is not a big concern.

Thus, for each fixed $ N>0$, the partial sum of the formal solution,  $ S_N(x)$, will satisfy the PDE and BC and will approximate the initial condition as accurately as we wish.

\section{Supplement: The Sound of Music}

\begin{eg}[space and time waves]
	For the general solution, if we fix a $ t$, then we get a space wave, which represents the physical position of the string at a specific time. If we fix a  $ x$, we get a time wave. which represents the evolution of each point of the string through time. 
\end{eg}

\subsection{Standing Waves}

The vertical displacement is a linear combination of the simple product solutions.

Each is called the "normal nodes of vibration" for $ n=1,2,\ldots$. And each mode has amplitude $ \sqrt{A_n^2+ B_n^2} $.

The nth normal node is called the "nth harmonic".

For each fixed $ t$, each node looks like a simple oscillation called a  \emph{standing wave}.

Note that the period of each mode (in time) is $ \tau_n = 2\pi \cdot  \frac{L}{n \pi c} = \frac{2L}{ nc}$.

So one cycle is completed every $ \tau_n$ thus the frequency is $ f= \frac{1}{\tau_n} = \frac{nc}{2L } = \frac{n}{\tau_1}$ for $ n=1,2,\ldots$

The sound produced consists of the superposition of these infinite frequencies.

\subsection{Music Theory}
See slides. This is common sense. $ E_2 $ is 2 octaves above $ E_0$. 

When we pluck guitar, at $ n=1$ we have the  \allbold{first harmonic} or the \emph{fundaemental mode:} $ A_1 \sin \left( \frac{ \pi x}{ L} \right) \cos \left( \frac{ \pi c t}{ L} \right)  $.

Assume $ \omega_1  = 82.41 $Hz. We cannot mute fundamental harmonic because it has no inner stationary points. 

At $ n=2$, the shape of the standing wave is determined by  $ \sin \left( \frac{ 2\pi x}{ L} \right) $, which has 1 inner stationary point (that never moves). Then the frequency is twice the fundamental harmonic. The amplitude is a quarter of the fundamental harmonic.

Similarly, $ n=3$, it has 2 inner stationary points. So we can mute the third harmonic at $ h=\frac{L}{3}$ or $ \frac{2L}{3}$.

\subsection{Fun Facts}
\begin{itemize}
	\item Each octave increase corresponds to a doubling of the frequency.
	\item For every octave the frequency doubles per 12 notes then the frequency per note increases by a factor of $ 1.06$.
\end{itemize}
\end{document}
