\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\newpage
\section{Heat Equation on $ \rr$}

\begin{equation*}
\begin{cases}
	\text{PDE: } \frac{\partial u}{\partial t} = k \frac{\partial^2 u}{\partial { x}^2} & x \in \rr, t>0 \\
	\text{"BCs": } u(x,t)< \infty  & \ \forall \ x \in \rr, t>0 \\
	\text{ICs: } u(x,0)= U(x) & \text{ where } \int_{-\infty}^{\infty} |U(x)|dx = M < \infty   \\
\end{cases}
\end{equation*}

Again PDE and BCs form a vector space so we can use separation of variables. Then we get

\begin{equation*}
\begin{cases}
	F''(x)= \lambda F(x)\\
	F(x) < \infty \ \forall \ x \in \rr, t>0\\
\end{cases}
\text{ and } G'(t) = \lambda k G(t)
\end{equation*}
\begin{note}[]
This $ \lambda$ has opposite sign as the one we used before.
\end{note}
If $ \lambda >0$, the solutions are not bounded. If $ \lambda = 0$, we have $ F_0(x) = B$. If  $ \lambda < 0$, we get $ \lambda = -m^2$ for nonzero $ m \in \rr$. And
\[
F_n=A_m e^{imx} + B_m e^{-imx} \text{ for } m \in \rr 
.\] 
For the time domain problem,
\[
	G'(t) = \lambda k G(t) \implies G_m(t) = G(0) e^{-m^2 kt} \text{ for } m \in \rr 
.\] 
Thus, summing over all product solutions with real numbers $ m \in \rr$ yields
\[
	u(x,t) = \int_{-\infty}^{\infty} a_m e^{imx} e^{-m^2kt} d m + \int_{-\infty}^{\infty} b_m e^{-imx} e^{-m^2kt} d m  
.\] 
\begin{note}[]
The complex exponential is oscillating whereas the real exponential is a time-decaying term.
\end{note}
Notice that the second integral is redundant, since we can just use a change of variable $ m=-p$ to get the same form. So
 \[
	 u(x,t) = \int_{-\infty}^{\infty} a_m e^{imx} e^{-m^2kt} d m  
.\]
To find $ a_m$, we use the IC:
 \[
	 U(x) = u(x,0) = \int_{-\infty}^{\infty} a_m e^{imx}d m \text{ and } U(x) = \int_{-\infty}^{\infty} \hat{ U}(m) e^{imx} d m \implies a_m = \hat{ U}(m)   
\] 
by form matching according to our theory. So we can use the Fourier transform as the coefficient. So the solution becomes
\[
	u(x,t) = \int_{-\infty}^{\infty} \hat{ U}(m) e^{imx}e^{-m^2kt} d m
\]
where
\[
	\hat{ U}(m) = \frac{1}{2\pi} \int_{-\infty}^{\infty} U(x) e^{-imx} dx 
.\] 
Note that $ \hat{ U}(0) = \frac{1}{2\pi} \int_{-\infty}^{\infty} U(x) dx$ which is the area under the IC curve divided by $ 2\pi$.  Intuitively this is like area divided by something like a length.

$ \hat{ U}(x)$ is bounded because by boundedness of the integral of $ U(x)$
\[
	|\hat{ U}(m)| \leq \frac{1}{2\pi} \int_{-\infty}^{\infty} |U(x)| \cdot |e^{-imx}| dx = \frac{1}{2\pi} \int_{-\infty}^{\infty} |U(x)|dx \leq \frac{M}{2\pi}  
.\] 

\begin{remark}
This is part of the \emph{Riemann-Lebesgue Lemma} for Fourier transform.  
\end{remark}

\begin{lem}[Riemann-Lebesgue for Fourier transform]
	Suppose $ U(x)$ is defined on  $ -\infty<x<\infty$ and let
	\[
		\hat{ U}(m) = \mathcal{F}[U(x)] = \frac{1}{2\pi} \int_{-\infty}^{\infty} U(x) e^{-imx} dx, \ \forall \ m \in \rr 
	.\] 
	If $ \int_{-\infty}^{\infty} |U(x)| dx = M < \infty$, then
	\begin{enumerate}[label=\arabic*)]
		\item $ \hat{ U}(m)$ is bounded and $ \hat{ U}(m) \leq \frac{M}{2\pi}$.
		\item $ \hat{ U}(m)$ is continuous for all real $ m$.
		\item  $ \hat{ U}(m) \to 0$ as $ m \to \infty$.
	\end{enumerate}
\end{lem}
\begin{note}[]
	This is a special case. Intuitively if the IC is "well-behaved". then the Fourier transform is also well-behaved. Then we can truncate $ \hat{ U}(m)$ without much loss of information.
\end{note}

\begin{prf}
~\begin{enumerate}[label=\arabic*)]
	\item See previous.
	\item Given real number  $ m_n$, define $ U_n(x) = U(x) e^{-im_n x}$ then $ \ \forall \ x \in r$, we have
		\[
			\lim_{ n \to \infty} U_n(x) = \lim_{ n \to \infty} U(x) e^{-im_n x} = U(x) e^{-imx}, |U_n(x)|\leq |U(x)| \ \forall \ n
		.\] 
		Thus by \emph{Lebesgue Dominated Convergence Theorem}, this result yields
		\[
		 \lim_{ n \to \infty} \int_{-\infty}^{\infty} U_n(x) dx = \int_{-\infty}^{\infty}  U(x) e^{-imx} dx \implies \lim_{ m_n \to m} \hat{ U}(m_n) = \hat{ U}(m) 
		.\] 
		Thus $ \hat{ U}(m)$ is continuous.
	\item We will only prove 3 for the simple case that $ U(x)$ is the indicator function over the set  $ [-L,L]$:
		 \begin{equation*}
			 U(x)=
		\begin{cases}
			1, &\text{ if } x \in [-L,L] \\
			0, & \text{ otherwise}\\ 
		\end{cases}
		\end{equation*}

		Then
		\begin{align*}
			\left| \int_{-\infty}^{\infty} U(x) e^{-imx}  \right| &= \left| \int_{-L}^{L} e^{-imx}  \right|  \\
			&= \left| \frac{e^{-imL} - e^{imL}}{ -im} \right|  \\
			&\leq \frac{|i^{e^{-imL}}| + |i e^{imL}|}{|m|}  \\
			&= \frac{2}{|m|} 
		\end{align*}
		By Squeeze Theorem, taking $ m \to \pm \infty$, this bound gives us
		\[
			\lim_{ m \to \pm \infty} \int_{-\infty}^{\infty} U(x) e^{-imx} dx = 0 \implies \hat{ U}(m) \to 0 \text{ as } m  \to \pm \infty  
		.\] 
		Note that this result can be extended to any function $ U(x)$ such that  $ \int_{-\infty}^{\infty} |U(x)|dx < \infty$. Such result is the \emph{Riemann-Lebesgue Theorem}.  
\end{enumerate}
\end{prf}
\end{document}
