\documentclass[12pt]{article}
\input{../preamble.tex}

\begin{document}
\centerline {\textsf{\textbf{\LARGE{Homework 5}}}}
\centerline {Jaden Wang}
\vspace{.15in}

\begin{problem}[9.1]
Let's start tracing the orbit from 1: $ \{1,5,2\} $.\\
3: $ \{3\} $.\\
4: $ \{4,6\} $ \\
The orbits are: $ \{1,5,2\}, \{3\},\{4,6\}. $
\end{problem}
\begin{problem}[9.2]
1: $ \{1,5,8,7\} $.\\
2: $ \{2,6,3\} $.\\
4: $ \{4\} $.\\
The orbits are: $ \{1,5,8,7\}, \{2,6,3\},\{4\} $.
\end{problem}

\begin{problem}[9.7]
\begin{align*}
	\text{(1 4 5)(7 8)(2 5 7)}&=\text{(1 4 5 8 7 2)}\\
				  &= \begin{pmatrix} 1&2&3&4&5&6&7&8\\4&1&3&5&8&6&2&7 \end{pmatrix}   \\
\end{align*}
\end{problem}
\begin{problem}[9.8]
\begin{align*}
	\text{ (1 2)(4 7 8)(2 1)(7 2 8 1 5)} &= \text{(1 5 8)(2 4 7)} \\
					     &= \begin{pmatrix} 1&2&3&4&5&6&7&8\\5&4&3&7&8&6&2&1 \end{pmatrix}  \\
\end{align*}
\end{problem}
\begin{problem}[9.10]
By tracing the orbits we can rewrite the permutation as a product of disjointed cycles:\\

(1 8)(3 6 4)(5 7) = (1 8)(3 4)(3 6)(5 7).
\end{problem}

\begin{problem}[9.11]
	(1 3 4)(2 6)(5 8 7) = (1 4)(1 3)(2 6)(5 7)(5 8)
\end{problem}
\begin{problem}[9.23]
~\begin{enumerate}[label=\alph*)]
	\item False. A cycle requires at least one orbit with more than one elements. So the identity permutation is not a cycle.
	\item True. By definition.
	\item False. 9.15 eliminated a case when a permutation is both a product of even number and product of odd number of transpositions, so we don't have to consider such case in 9.18. 
	\item True. By Corollary 9.12, since a nontrivial subgroup of $ S_9$ contains permutations of at least two elements, they must be a product of transpositions. Hence some transpositions must be in the subgroup.
	\item False. $ |A_5|=5!/2=60$.
	\item False. $ S_1 = \{id\} $ is trivially cyclic with $ id$ as the generator.
	\item True.  $ |A_3|=3!/2=3$. We know that all groups with order 3 are isomorphic to $ \zz_3$ and it is commutative. So $ A_3$ must be isomorphic to that group and be commutative too.
	\item True. By fixing 8 we are only permuting 7 elements. This is isomorphic to $ S_7$.
	\item True. Same as above.
	\item False. The identity is an even permutation so this set of only odd permutations cannot be a subgroup.
\end{enumerate}
\end{problem}
\begin{problem}[9.24]
	$ A_3$ are:
\begin{align*}
	\rho^0 &= \text{ (1 2)(1 2)}  \\
	\rho^1 &= \text{(1 2 3)} = \text{(1 3)(1 2)} \\
\rho^2 &= \text{(1 3 2)} = \text{(1 2)(1 3)}  \\
\end{align*}
which are all products of even number of transpositions.
\begin{table}[H]
	\centering
	\begin{tabular}{c||c|c|c}
	& $ \rho^0 $ & $ \rho^1$ & $ \rho^2$\\
	\hline
	\hline
		$ \rho^0 $& $ \rho^0$ & $ \rho^1$ & $ \rho^2$\\
		\hline
		$ \rho^1 $ & $ \rho^1$ & $ \rho^2$& $ \rho^0$\\
		\hline
		$ \rho^2 $ & $ \rho^2$& $ \rho^0$ & $ \rho^1$\\

	\end{tabular}
\end{table}
\end{problem}
\end{document}
