\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\begin{eg}[]

Question: Are 19 and 6 in the same coset?

No, because $ x+H=y+H \iff x-y \in H$. And $19-6=13 \not\in H$. 

Are 19 and 7 in the same coset?

Yes, because $ 7-19=-12 \in H$.

\end{eg}

\begin{eg}[easiest one: left/right cosets are different, IMPORTANT]
	$ G=S_3$,  $ H=\{e, (1\ 2)\} $. 

	What are the left cosets of $ H$ in  $ G$?
	 \begin{enumerate}[label=\arabic*)]
		\item H itself.
		\item The left coset containing $ (1\ 2\ 3)H = \{(1\ 2\ 3)e, (1\ 2\ 3)(1\ 2)\} =\{(1\ 2\ 3), (1\ 3)\}  $.
		\item by elimination, we know the last left coset is $ \{(2\ 3),(1\ 3\ 2)\} $.
	
	\end{enumerate}
			Question: is $ (1\ 3\ 2)H=(2\ 3)H$? Yes because let  $ x= (1\ 3\ 2)$ and  $ y=(2\ 3)$, then  $ x^{-1}= (1\ 2\ 3)$, so $ x^{-1}y=(1\ 2\ 3)(2\ 3)=(1\ 2) \in H$.
			QUestion: is $ (1\ 2\ 3)H=(2\ 3)H$?  $ x^{-1}y=(1\ 3\ 2)(2\ 3) = (1\ 3) \not\in H$, so no.

We can just take every element of the left cosets and individually invert it to convert to right cosets. 

Show that $ H(1\ 3)=H(1\ 3\ 2)$.  $ xy^{-1}=(1\ 3)(1\ 2\ 3)=(1\ 2) \in H$.

\end{eg}
\begin{eg}[]
	$ G=S_3, H=\{e\}  $. There are six cosets. Left/right cosets are the same even if the group is nonabelian.
\end{eg}

\begin{eg}[]
	$ G=S_3,H=S_3$. There is only one coset (left/right).
\end{eg}
\begin{eg}[]
	$ G=S_3, H=A_3$. There are two cosets. Left and right again agree because there is a subgroup and everything else.
\end{eg}
\begin{claim}[]
	Left and right cosets always agree if there are only two cosets (because one must a subgroup).
\end{claim}

\begin{thm}[]
	If $ G$ is finite, then the order of  $ x$, $o(x)$ divides  $ |G|$.
\end{thm}
\begin{prf}
$ \langle x \rangle$ is a subgroup of $ G$, so  $ |\langle x \rangle|$ divides $ G$ by Lagrange.
\end{prf}

\begin{thm}[10.11]
Every group of prime order is cyclic.
\end{thm}
\begin{eg}[]
We know this doesn't have to be true for non-prime number: $ V_4$.
\end{eg}
\begin{prf}
Let $ G$ be a group of order  $ p$ and let  $ H\geq g$. Then  $ |H|$ divides  $ |G|$. But since  $ |G|$ is a prime, so  $ |H|=1 \implies H=\{e\} $ or  $ |H|=p \implies H=G$.
\end{prf}

\begin{claim}[]
Let $ x \in G\setminus \{e\} $. Then $ \langle x \rangle =G$. Not only is $ G$ cyclic, but any nonidentity element is a generator.
\end{claim}

\begin{defn}[direct products]
	Let $ (G,*_G)$ and  $ (H,*_H)$ be two groups. The \allbold{direct product} $ G \times H$ as
	\[
		G \times H= \{(g,h):g \in G, h \in H\} 
	.\] 
	Operation: componentwise
	\[
		(g_1,h_2) * (g_2,h_2) = (g_1*g_2,h_1*h_2)
	.\] 
	where closure follows immediately.
	
	Identity: $ e = (e_G,e_H)$.  $ (e_G,e_H)*(g,h) = (e_G*g,e_H*H)=(g,h)$. Same for the other way.

	Inverse:  $ (g^{-1},h^{-1})$.

	Associativity: see book.
\end{defn}

\begin{eg}[]
$ \zz_2 \times \zz_2$ under $ +_2$. See iPad screenshots for the table. $ |A \times B|=|A| \times |B|$. It is isomorphic to $ V_4$. This is the proof that $ V_4$ is a group and is associative. 

Therefore, $ \zz_2 \times \zz_2$ is NOT isomorphic to $ \zz_4$!
\end{eg}
\begin{eg}[]
	$ \zz_2 \times \zz_3$ this is an abelian group of order 6. $ x=(1,1) \in \zz_2 \times \zz_3$. $ x + x = (0,2)$.  $ x+x+x=(1,0)$.  $ 4x = (0,1)$.  $ 5x=(1,2)$.  $ 6x=(0,0)$. Hence $ \zz_2 \times \zz_3$ is generated by $(1,1)$. So it is a cyclic group of order 6. Then it must be isomorphic to  $ \zz_6$! 
\end{eg}
\begin{claim}[]
Direct product of abelian groups are abelian.
\end{claim}
\begin{claim}[]
	$ \zz_m \times \zz_n \simeq \zz_{mn}$ if and only if $ \gcd ( m,n)=1 $. If $ \gcd ( m,n) =1$, then the order of $ (1,1)$ is  lcm$(m,n)=mn $.
\end{claim}

Goal: classify all abelian groups of order $ n$.

\end{document}
