\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\section{}
\begin{note}[]
Every subgroup of an abelian group is abelian.
\end{note}
\begin{thm}[]
Let $ G$ be a group and  $ H_1,\ldots,H_k$ be subgroups of $ G$. Then $ H_1 \cap \ldots \cap H_k \cap  \ldots$ is a subgroup of $ G$.
\end{thm}
\begin{prf}
\begin{enumerate}[label=(\roman*)]
	\item $ e \in H_i$ for all $ i$, so $ e \in \bigcap H_i$
	\item Let $ x,y \in \bigcap H_i$, then for each $ i$, $ x \in H_i$ and $ y \in H_i \implies \text{ for each } i,x*y \in H_i \implies x*y \in \bigcap H_i$.
	\item for each $ i$,  $ x \in H_i \implies \text{ for each }i, x^{-1} \in H_i \implies x^{-1} \in \bigcap H_i$.
\end{enumerate}
\end{prf}

\begin{note}[]
Unions of subgroups are usually not subgroups, since $ x*y $ might not be in the set.
\end{note}

\begin{thm}[]
Let $ G$ be a group and let  $ a_1,a_2,\ldots,a_k$ be elements of $ G$. Then there is a smallest subgroup $ H$ of $ G$ that contains  $ a_1,\ldots,a_k$. 
\end{thm}
\begin{note}[]
Smallest means that every other subgroups contains this subgroup.
\end{note}
\begin{prf}
Take all such subgroups and intersect them. Then 
\[
H = \bigcap H_i
.\]
is the smallest subgroup. $ H_i$ is well-defined because at least $ G$ is such subgroup.
\end{prf}

\begin{thm}[]
	Let $( G,*)$ be a group. Let  $ a,b,c \in G$. Let $ H$ be the smallest subgroup containing  $ a,b,c$. Then,  $ H=\langle a,b,c \rangle$.  
\end{thm}
\begin{eg}[]
A word in the generators and their inverses: $a^{-2}b^3ca^{-1}c^{-1}b^2a^{-3} $. This lies in $ H$.
\end{eg}
\begin{thm}[]
The set of "words in the generators and their inverses" forms a subgroup.
\end{thm}
\begin{prf}
\begin{enumerate}[label=(\roman*)]
	\item $ a_1 a_1^{-1}$ the identity is a word.
	\item Closure: juxtaposition gives another word.
	\item Inverses: just another word.
\end{enumerate}
\end{prf}
\begin{thm}[]
The words $ a_1,\ldots,a_k$ and their inverses is the smallest subgroup containing $ a_1,\ldots,a_k$.
\end{thm}

\begin{prf}
We want to show that $ H = \langle a,b,c \rangle = \bigcap H_i$. 
\end{prf}
\begin{intuition}
	The intersection starts big and the generator starts small. They both give the same result.
\end{intuition}

\begin{defn}[finitely generated]
	If there exists a finite set $ \{a_1,\ldots,a_k\} $ of elements in $ G$ with  $ G=\langle a_1,\ldots,a_k \rangle$, we call  $ G$  \allbold{finitely generated}. 
\end{defn}

\begin{eg}[]
$ V_4$. 
 $ H=\langle a,b \rangle$. Then
 \[
 H=\{e,a,b,c\} 
 .\] 
 So $ V_4$ can be generated by 2 elements but not 1 element.
\end{eg}

\begin{note}[]
	Every finite group is finitely generated. Just take all elements as generators.
\end{note}

\begin{eg}[]
	$ \zz$ is an infinite group that is finitely generated.  $ \zz = \langle 1 \rangle$.
\end{eg}
\begin{eg}[Challenge]
	Show that $ \qq$ is not finitely generated.
\end{eg}

\begin{eg}[Figure 7.11(b)]
See iPad.
\end{eg}
\end{document}
