\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

What are the cosets of kernel?
\begin{document}
\begin{thm}[]
	Let $ \phi:G \to H$ be a homomorphism, and $ K= \ker \phi = \{x \in G: \phi(x)=e_H\} $. The left and right cosets of $ K$ are the same. That is,
	\[
	xK = yK \iff Kx=Ky
	.\] 
\end{thm}

\begin{prf}

\begin{note}[]
$ xK = yK \iff x^{-1}y \in K$.
\end{note}
Thus $ x^{-1}y \in \ker \phi \iff \phi(x^{-1}y)=e_H \iff \phi(x)^{-1} *_H \phi(y) =e_H$. Therefore, $ xK = yK \iff \phi(x) = \phi(y)$. Similarly, $ Kx=Ky \iff \phi(x)=\phi(y)$.
\end{prf}

\begin{defn}[normal subgroup]
Let $ H \leq G$. We say  $ H$ is a  \allbold{normal subgroup} of $ G$ if the left and right cosets of  $ H$ in $ G$ agree. We denote this as $ H \trianglelefteq G$.
\end{defn}
\begin{note}[]
There is no such thing as a "normal group". It only applies to subgroups.
\end{note}

\begin{claim}[]
~\begin{itemize}
	\item If $ G$ is a group then  $ G \trianglelefteq G$.
	\item The trivial subgroup $ \{e\} $ is a normal subgroup.
	\item If $ G=S_3$ and $ H=\{e,(1\ 2)\} $, then $H$ is not normal in $ G$. This is the smallest example of non-normal subgroup. (even though $ H$ is abelian!)
	\item If $ G$ is abelian and  $ H \leq G$ then  $ H \trianglelefteq G$. "Any subgroup of an abelian group is normal."
	\item Any group $ G$ has normal subgroups  $ G$ and  $ \{e\} $.
	\item \allbold{EVERY SUBGROUP OF INDEX 2 IS NORMAL}.
		\begin{prf}
			Suppose $ H \leq G$ and  $ H$ has index 2 (number of cosets). Then the left cosets are:  $ H$ and everything else. The right cosets are again  $ H$ and everything else. Therefore they must agree.
		\end{prf}
	\item The kernel of a homomorphism is a normal subgroup.
\end{itemize}
\end{claim}

\begin{eg}[determinant map]
	$ \phi : GL_N( \rr) \to \rr^*, \phi(A)= \det A $. $ \ker \phi= \{A \in GL_n( \rr): \phi(A) = 1\} = \{A \in GL_n( \rr): \det A = 1\} = SL_n( \rr)$, the special linear group. 

	Is $ SL_n( \rr) \trianglelefteq Gl_n( \rr)$? Yes, because it's the kernel of a homomorphism.
\end{eg}

\begin{eg}[sign map]
$ \ker \varepsilon = A_n$ so $ A_n \trianglelefteq S_n$ because 1. it's the kernel of a known homomorphism 2. index of $ A_n$ in $ S_n$ is 2.
\end{eg}

\end{document}
