\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\section{Permutation Groups}
~\begin{defn}
	Let $ A $ be a set (e.g. $ A = \{1,2,3,4,5\} $). A \allbold{permutation} of $ A$ is a bijective function $ \sigma: A \to A$.
\end{defn}

\begin{thm}[]
	A function is bijective if and only if it has a two-sided inverse (i.e. the function is invertible).
\end{thm}

\begin{thm}[]
	A function between two finite sets with the same number of elements is injective if and only if the function is surjective.
\end{thm}

\begin{eg}[]
$ A=\{1,2,3\} $. A permutation of $ A$ might be \ldots. There are 3! permutations. There are $ n!$ permutations of an $ n$-element set.
\end{eg}

\begin{thm}[permutation group]
Let $ A$ be a set. The set permutations of  $ A$, denoted by  $ S_A$ is a group under composition of functions.
\end{thm}
\begin{claim}[]
$ \tau \circ \sigma$ is a permutation of $ A$.
\end{claim}
\begin{prf}
Let $ \sigma, \tau$ be permutations of $ A$. So  $ \sigma$ has a two-sided inverse, $ \sigma^{-1}$, and so does $ \tau$, $ \tau^{-1}$. The inverse of $ \tau \circ \sigma$ is $ \sigma^{-1} \circ \tau^{-1}$. This gives bijectivity.
\end{prf}

\begin{prf}
To show it's a group, 
\begin{enumerate}[label=\arabic*)]
	\item the identity of $ A$ is  id$_A$ where  id$_A(a)=a $. 
	\item the inverse is $ \sigma^{-1}$.
	\item composition of functions is associative.
	\item the previous claim shows that it is closed under operation.
\end{enumerate}
\end{prf}

\begin{defn}[symmetric group]
$ S_A$ is the  \allbold{symmetric group} on $ A$. If  $ A=\{1,\ldots,n\} $, we write $ S_n$ for  $ S_A$. It has the order  $ n!$.
\end{defn}

\begin{eg}[]
$ S_3$ permutations of  $ \{1,2,3\} $ with 6 elements. See iPad. $ S_3$ is a nonabelian group with order 6, which is the smallest nonabelian group.  $ V_4$ is the smallest noncyclic group.
\end{eg}


\end{document}
