\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
Homework 8: To check whether a group is isomorphic to $ V_4$, we can check whether two unique non-identity elements square to the identity. To tell if two cosets are different, check if their difference is in the subgroup.

\begin{eg}[]
	Not assuming multiplication is commutative.
	\begin{align*}
		(1+1)(a+b) &= (1+1)a+(1+1)b = a+a+b+b\\ 
			   &=1(a+b)+1(a+b)= a+b+a+b. 
 \end{align*}
 So commutativity of addition is forced by multiplicative identity and distributive laws.
\end{eg}

What if we had $ 1_R=0_R$?

\begin{thm}[18.8]
\begin{enumerate}[label=(\roman*)]
	\item $0a=a0=0$.
	\item $a(-b)=(-a)b=-(ab)$.
	\item $ (-a)(-b)=ab$.
\end{enumerate}
\end{thm}
\begin{prf}
~\begin{enumerate}[label=(\roman*)]
	\item \[
			0a=(0=0)a=0a+0a \implies y=y+y 
	\] 
	by an abelian group. Then $ 0=y=a0$. Likewise for the other.
\item 
	 \[
		 0=a0=a(b+(-b))=ab+a(-b) \implies a(-b) = -(ab)
	.\] 
	Likewise for the other.
\item \[
		(-a)(-b)= -((-a)b)=-(-(ab))=ab
.\] 
\end{enumerate}
\end{prf}

If $ 1_R=0_R \implies 1_R r = 0_R r \implies r=0_R$. Then $ R=\{0_R\} $. This is why we restrict them to be different.

\begin{note}[]
If $ A$ is an abelian group, we can make  $ A$ into a ring in a dull way.

Set:  $ A$. Addition: addition in  $ A$. Multiplication:  $ a\times b=0$. We can check this is a ring.
\end{note}
\begin{eg}[]
	$ R=\{f: \rr \to \rr\} $. 

	Addition: pointwise. $ (f+g)(c)=f(c)+g(c)$.  

	Multiplication: pointwise. $ (fg)(c)=f(c)g(c)$.

	We can check this is a ring (vector space). Let check a distributivity law. Two functions are the same if they always give the same output for the same input.

	 \begin{align*}
		 ((f+g)(h))(c) &=  (f+g)(c) h(c)\\
			       &= (f(c)+g(c))h(c) \qquad \text{ just real numbers} \\
			       &=  f(c)h(c)+g(c)h(c)\\
			       &= fh(c)+gh(c) \\
			       &= (fh+gh)(c) 
	\end{align*}
	They are the same because real numbers are distributive.

Is $ R$ commutative? Yes.

Does $ R$ have identity? $ 1_R$.

\end{eg}
\begin{remark}
	Composition of functions doesn't distribute over addition. 

	$ f(x)=x^2, g(x)=\sin(x ), h(x)=e^{x}$. Then
	\[
		f(g+h)=(\sin x e^{x})^2 \neq \sin^2 x + e^{2x} = fg+fh
	.\] 
\end{remark}

\begin{defn}[homomorphism of rings]
A map $ \phi: R \to S$ is a \allbold{homomorphism of rings} if
\[
	\phi(a+b) = \phi(a)+\phi(b)
\] 
\[
	\phi(a \times b) = \phi(a) \times \phi(b)
\] 
for all $ a,b \in \rr$.
\end{defn}

\begin{eg}[]
	$ \phi: \zz \to \zz, a \mapsto 2a$. We can find a counterexample for multiplication:

	$ \phi(1 \times 1)= 2 \neq 4 = \phi(1) \times \phi(1)$.
\end{eg}
\end{document}
