\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\begin{eg}[]
	Subgroups of $ S_3$: $ \{e, (1\ 2)\}, \{e,(1\ 3)\}, \{e,(2\ 3)\}, \{e\}, S_3, A_3$. The first three are not normal. The rest are normal. $ A_3$ is 1. index is two. 2. kernel of the sign homomorphism. 
\end{eg}

Let $ g \in G$, we have seen that if $ H \leq G$, then so is  $ gHg^{-1}$. Furthermore, the map $ \iota_g (x) = gxg^{-1}$ (injective map) is called conjugating by $ g$.  
\begin{prop}[]
	$ \iota_g$ is a group homomorphism (in fact an isomorphism) from  $ G$ to itself.
\end{prop}
\begin{prf}
\begin{align*}
	\iota_g(xy)=gxyg^{-1} = gxg^{-1}gyg^{-1}=\iota_g(x) \iota_g(y)
\end{align*}
\end{prf}
\begin{eg}[]
Isomorphism of $ V_4 \to V_4$. Identity needs to go to itself, but there are 3! different isomorphism. Then the group of isomorphisms are just $ S_3$. 

But since it's abelian, conjugation is trivial.
\end{eg}

\begin{claim}[]
	The inverse of $ \iota_g = \iota_{g^{-1}}$ (conjugation by  $ g^{-1}$ ).
\end{claim}

\begin{defn}[automorphism]
An isomorphism from $ G$ to itself is called an  \allbold{automorphism}. 
\end{defn}

\begin{defn}[inner automorphism]
Automorphisms that come from conjugation are called \allbold{inner automorphism}. 
\end{defn}
\begin{note}[]
Inner automorphism is a subgroup of the group of automorphisms
\end{note}

\begin{note}[]
	$ \iota_g(H)$ is a subgroup of  $ G$ because it is the image of  $ \iota_g$.
\end{note}
\begin{defn}[]
\[
H \simeq gH g^{-1}
.\] 
is conjugate subgroup.
\end{defn}

\begin{eg}[]
	$ G=S_3, H=\{e, (1\ 2)\}, g=(1\ 3) $. Then
\begin{align*}
	gHg^{-1} &= \{geg^{-1}, g(1\ 2)g^{-1}\}\\
		 &= \{e, (2\ 3)\}  \\
	gHg^{-1} &\simeq H \text{ but } H \neq gHg^{-1} 
\end{align*}
Which proves that $ H$ is not normal.
\end{eg}

\begin{thm}[]
If $ G$ is abelian, then  $ G / N$ is abelian.
\end{thm}
\begin{prf}
Let $ xN,yN \in G / N$. Then
\begin{align*}
	xN*yN= (xy) N = (yx) N = yN*xN
\end{align*}
Since $ x=y \implies xN = yN$.
\end{prf}
\begin{note}[]
The converse is false. Example is $ S_3 / A_3$. Or the trivial $ N$.  
\end{note}
\begin{note}[]
$ G / N$ is cyclic doesn't imply $ G$ is cyclic.
\end{note}

What is the order of $ xN \in G / N$? It is the smallest $ n>0$  such that $ (xN)^{n}=N \implies x^{n} N= eN \implies e^{-1}x^{n} \in N \implies x^{n} \in N$.

\begin{defn}[]
The order of a coset $ xN \in G / N$ is the smallest positive integer $ n$  such that $ x^{n} \in N$. 
\end{defn}

\begin{eg}[15.7]
$ G= \zz_4 \times \zz_6$. Order is 24. If $ G_1$ and $ G_2$ are abelian so is $ G_1 \times G_2$. If one group is not abelian, then the product isn't abelian. So $ G$ is abelian. $ G$ isn't cyclic since it isn't isomorphism to $ \zz_{24}$. 

$ H=\langle (0,1) \rangle = \{(0,0), (0,1),\ldots,(0,5)\} $. The order is 6. 

Is $ H$ normal in  $ \zz_4 \times \zz_6$? Yes because $ G$ is abelian.

Then  $ G / H$ is abelian with order 4. So it's either $ \zz_4$ or $ V_4$. We can show $ \zz_4$ if we find an element of order 4 (a generator). Then a coset looks like  $ (1,0)+ \langle (0,1) \rangle$. 

What is the order of that? 

First find all elements of $ N$. Then repeat operation on the representative of coset until it's in  $ N$.  It takes 4 steps to get $ (0,0) \in N$. Thus it has order 4.
\end{eg}
\begin{eg}[]
	$ \qq / \zz$ is an infinite group where every element has finite order.

	$ \rr / \qq$ is an infinite group that has no element of finite order apart from the identity.

	$ \rr / \zz \simeq U$. Since $ \phi: \rr \to C^*, r\mapsto e^{2\pi i r} $.
\end{eg}
\end{document}
