\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
$ x$ commutes with everything.
Multiplication:
\[
	\left( \sum_{ i= 0}^{ n} a_i x^{i} \right) \left( \sum_{ j= 0}^{ n} b_j x^{j} \right) = \sum_{ k= 0}^{ n} c_k x^{k} 
\]
where 
\[
c_k = \sum_{ i= 0}^{ k} a_i b_{k-i}
.\] 

\begin{eg}[]
The coefficient of $ x^3$ is contributed by terms with degree up to 3. So $ c_3 = a_0 b_3 + a_1 b_2 + a_2 b_1 + a_3 b_0$.
\end{eg}

\begin{prop}[]
	The zero element in $ R[x]$ is the zero polynomial  $ 0_R$. If  $ R$ has identity, then so does  $ R[x]$: constant polynomial  $ 1_R$. If  $ R$ has zero divisors, then so does  $ R[x]$.
\end{prop}

\begin{eg}[]
	$ R=\zz_6, \zz_6[x]$. $ 2\times 3=0$, then think of these as constant polynomials, so they are zero divisors of $ R[x]$.
\end{eg}

\begin{thm}[]
	If $ R$ is a domain, then  $ R[x]$ is a domain.
\end{thm}
\begin{prf}
\begin{enumerate}[label=(\roman*)]
	\item $ R[x]$ is commutative, we can show by doing multiplication the other way around.
	\item  $ R[x]$ has identity: we can check  $ 1_R$ is the identity.
	\item  $ R[x]$ has no zero divisors: Suppose  $ f(x),g(x) \in R[x]$ and $ f(x) \neq 0, g(x)\neq 0$. We need to show that  $ f(x)g(x)\neq 0$.

		Let  $ f(x)$ have degree  $ n$ and  $ g(x)$ have degree  $ m$. So  $ f(x)=a_n x^{n}+ \ldots, a_n\neq 0$, $ g(x) = b_m x^{m}+ \ldots, b_n \neq 0$. So
		\[
			f(x)g(x)=a_n b_m x^{m+n}+\ldots
		.\] 
		Then $ a_n b_m \neq 0$ because $ R$ is a domain and  $ a_n, b_m \neq 0$.
\end{enumerate}
\end{prf}

\begin{coro}[]
	If $ R$ is a domain and  $ f(x),g(x) \in R[x]$ are nonzero, then deg$(f(x)g(x)) $ = deg$f(x) $+deg$g(x) $.
\end{coro}

\begin{eg}[counterexample when $ R$ is not a domain]
	$ \zz_6[x]$. Consider
	\begin{align*}
		(1+2x)(1-x+3x^2) &= 1-x+3x^2+2x-2x^2 +6x^3 \\
		&= 1+x+x^2 \\
	\end{align*}

	Is $ x^{6} = x^{0}$? No because coefficient of $ x^{6}$ is 1 but that of $ x^{0}$ is 0. 
	\begin{note}[]
	The exponents are not ring elements. They are natural numbers.
	\end{note}
\end{eg}

What are the units in $ R[x]$? 

If  $ R$ is not a domain, there is no easy answer.

If  $ R$ is a domain, the units in  $ R[x]$ are the constant units in  $ R$.

 \begin{eg}[]
	 $In \qq[x]$, the units are the nonzero constants because units in $ \qq $ are $ \qq \setminus \{0\} $.
\end{eg}
\begin{eg}[]
	The units in $ \zz_5[x]$ are $ \{1,2,3,4\} $. The units in $ \zz[x]$ are $ \pm 1$.
\end{eg}

\begin{thm}[]
	If $ R$ is a domain, then  $ U(R[x])=U(R)$.
\end{thm}

\begin{prf}
	Suppose $ f(x)g(x)=1$ (they are units). The degree 0 polynomials are the nonzero constant polynomials. The degree of 1 is 0, and equals to the sum of degrees of  $ f,g$, thus  $ f,g$ has degree 0 too. This means that  $ f(x),g(x)$ are nonzero constants, so they are units in  $ R$.
\end{prf}
\end{document}
