\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
Midterm 2 covers HW 5-8.

\section{Rings}

\begin{defn}[ring]
Let $ R$ be a set and define two binary operations,  $ +_{ R}, \times_R $ as following:

$\ \  \qquad  +_{ R} $ : $ R$ is an abelian group under  $ +_{ R} $.
\begin{enumerate}[label=\arabic*)]
	\item $ +_{ R} $ is a binary operation.
	\item $ +_{ R} $ is associative.
	\item $ +_{ R} $ has an identity, $ O_R$.
	\item Everything element  $ r$ has an additive inverse,  $ -r$.
	\item  $ +_{ R} $ is commutative.

$ \times_R $: $ R$ is closed under an associative multiplication.
	\item $ \times_R $ is a binary operation.
	\item $ \times _R$ is associative.

Axioms governing how the two operations interact.
\item left distributivity law: $ $
\[
 a \times _R(b+_{ R}c ) = a\times _R b + a\times _R c
.\] 
\item right distributive law:
	\[
		(a+_{ R} b )\times _R c = a \times _R c +_{ R} b \times _R c  
	.\] 
\end{enumerate}
\end{defn}
\begin{eg}[]
	$ (\zz, +_{ R}, \times _R) $ the ring of integers. This is a ring because we assume the axioms are true for addition and multiplication of complex numbers. The same goes for rational, real, and complex numbers.

	Additional properties they have:
	\begin{itemize}
		\item commutative multiplication: "commutative ring".
		\item multiplicative identity, $ I_R$, exists and $I_R = O_R$: "ring with identity".
	\end{itemize}
\end{eg}

\begin{eg}[]
$ 2\zz$, even integers under the usual operations. It is commutative but doesn't have multiplicative identity. Suppose $ I_R= 2k$, then $ 2k \times 2 \implies 4k= 2 \implies k=\frac{1}{2} \not\in 2\zz$. 
\end{eg}

\begin{eg}[]
	$ (\zz_6, +_{ 6},\times _6 )$ is a ring (prove by quotient ring). A subset $ \{0,3\} $. 
	\begin{table}[H]
		\centering
		\begin{tabular}{c|c|c}
			$ +_{ 6} $ & 0&3\\
			\hline
			0&0&3\\
			\hline
			3&3&0
		\end{tabular}
	\end{table}
	\begin{table}[H]
		\centering
		\begin{tabular}{c|c|c}
		 $ \times _6$ &0  &3\\
		 \hline
		 0&0&0\\
		 \hline
		 3&0&3
		\end{tabular}
	\end{table}
	The subring is commutative and has an identity of $ 3$, even though the identity from the ring is not here.
\end{eg}
\begin{eg}[]
	$ M_n( \rr)$ $ n \times n$ matrices with real entries under matrix addition and matrix multiplication. It is in fact a vector space of order $ n^2$. This is also a ring. So are $ M_n( \zz), M_n( \qq), M_n( \cc)$. 

	Are they commutative? No for $ n\geq 2$. Use the usual counterexample.

	Do they have an identity? Yes, $ I_n$.

	\begin{note}[]
		$ M_n(2 \zz)$: not commutative and no identity.
	\end{note}
\end{eg}
\end{document}
