\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\section{Orbits, Cycles, and the Alternating Groups}

\begin{note}[equivalence relation]
Reflexive: $ aRa$ for all  $ a \in S$.
Symmetric: If $ aRb$ then  $ bRa$.
Transitive: If  $ aRb$ and  $ bRc$ then  $ aRc$.
\end{note}

\begin{eg}[]
\[
	\sigma= \begin{pmatrix} 1&2&3&4&5&6&7&8\\3&8&6&7&4&1&5&2 \end{pmatrix} 
.\] 
See iPad for orbits.
Orbits of $ \sigma$ (sets) are: $ \{1,3,6\},\{2,8\} ,\{4,5,7\}  $. They are disjoint, their union is the whole set, they are a partition of $ \{1,2,\ldots,8\} $.
\end{eg}
\begin{defn}[]
	We define an equivalence relation on $ \{1,\ldots,8\} $. $ a\sim b$ if  $ b= \sigma^{n}(a)$ for some $n \in \zz$.
\end{defn}

\begin{claim}[]
$ \sim$ is an equivalence relation.
\end{claim}
\begin{prf}
	Reflexive: Take $ n=0$,  $ a = \sigma^{0}(a)$.\\
	Symmetric: If $ b= \sigma^{n}(a)$ then $ a = \sigma^{-n}(b)$.\\
	Transitive: If $ b = \sigma^{n}(a)$ and $ c= \sigma^{m}(b)$ then $ c= \sigma^{n+m}(a)$.
\end{prf}

\begin{notation}[cycles]
	(1,3,6) or (1 3 6) means "1 maps to 3 which maps to 6, which maps back to 1". This is the same as (3 6 1) and (6 1 3). We prefer to use (1 3 6) where the smallest number to be in the front. This is called a cycle of length 3 or "3-cycle".
\end{notation}

\begin{eg}[other cycles of $ \sigma$]
	(2 8) = (8 2) "2-cycle (transposition)" and (4 7 5) = (7 5 4) = (5 4 7) "3-cycle". 
\end{eg}

\begin{notation}
	(4 7 5) means 
	\[
		\begin{pmatrix} 1&2&3&4&5&6&7&8\\1&2&3&7&4&6&5&8 \end{pmatrix} 
	.\] 
	So there is one orbit of length 3 and others are length 1. This permutation would be called "3-cycle". If a permutation has two orbits with more than one element, then it's not a cycle.
\end{notation}
\begin{eg}[]
\[
	\sigma = \begin{pmatrix} 1&2&3&4&5&6&7&8\\3&8&6&7&4&1&5&2 \end{pmatrix} = (1\ 3\ 6)(2\ 8)(4\ 7\ 5)
.\]
These are disjoint cycles (no elements are mentioned more than once). Any permutation can be written as a product of disjoint cycles.
\end{eg}

\begin{eg}[9.10]
$ S_6$. Consider
\[
	(1\ 4\ 5\ 6)(2\ 1\ 5)=(1\ 6)(2\ 4\ 5 )(3)
.\] 
We start with the smallest number in the permutation and go from right to left. We trace the mapping until they form a cycle, then we close the parenthesis and move on to the next smallest number that hasn't been traced.
\begin{note}[]
Disjoint cycles commute.
\end{note}

\[
	(2\ 1\ 5)(1\ 4\ 5\ 6) = (1\ 4\ 2)(3)(5\ 6)
.\] 

\end{eg}
\end{document}
