\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}

We can show one binary structure is a group if it is isomorphic to another group. Because the required properties for groups are all structural properties.

\section{Subgroups}
\begin{defn}[subgroup]
	Let $(G,*)$ be a group. Let  $H \subseteq G$. We call $H$ a subgroup of  $G$ if  $H$ is a group under the same operation.
\end{defn}

\begin{note}[]
Subspace in linear algebra is an example of subgroup.
\end{note}
\begin{eg}[]
	~\begin{itemize}
		\item $\zz$ is a subgroup of $\qq$ under addition.
	\item $U_{28}$ is a subgroup of $U$, where  $U$ is the unit circle under $\times $.
	\item $\zz_2$ is the integers mod 2 under $+_2$ is NOT a subgroup of $\zz$ because they don't have the same operation.
	\item $\{1,2,3,\ldots\} $ under addition is NOT a subgroup of the $\zz$ because there is no identity.
	\item $\{0,1,2,\ldots\}$ under $+ $ is NOT a subgroup of $\zz$ because $1$ doesn't have an inverse.
	\end{itemize}
\end{eg}

\begin{thm}[]
	Let $(G,*)$ be a group and let  $H \subseteq G$. Then $H\leq G$ if 
\begin{itemize}
	\item $e \in H$
	\item if $x \in H$ then $x^{-1} \in H$ 
	\item if $x,y \in H$, then $x*y \in H$
\end{itemize}
\end{thm}

\begin{note}[]
	Associativity is implied because it's the same operation. The first condition ensures that $H \neq \O$.
\end{note}

\begin{coro}[]
	Any group $G$ has the following as subgroups:
	 \begin{itemize}
		\item $G$ itself
		\item $\{e\} $
	\end{itemize}
\end{coro}

\begin{eg}[]
Find the subgroups of $V_4$. See iPad.

\begin{itemize}
	\item 4 elements: $\{3,a,b,c\} $ 
	\item 1 element: $\{e\} $ 
	\item 2 elements: $\{e,a\},\{e,b\} ,\{e,c\}  $
	\item 3 elements: nope
\end{itemize}
There are a total of 5 subgroups.
\begin{note}[]
In $V_4$, the smallest subgroup containing  $a$ is $\{e,a\} $. Likewise for other non-identity elements. The smallest subgroup for  $e$ is  $\{e\} $.
\end{note}
\end{eg}

\begin{eg}[]
Find the subgroups of $\zz_4$. See iPad.
\begin{itemize}
	\item $4$ elements:  $\{0,1,2,3\} $ 
	\item 1 elements: $0$ 
\item  $2$ elements: only $\{0,2\} $ works
\item 3 elements: nope
\end{itemize}
There are only 3 subgroups.
\begin{note}[]
In $\zz_4$ the smallest subgroup containing 2 is $\{0,2\} $, the smallest for 0 is $\{0\} $, the smallest for 1 or 3 is  $\{0,1,2,3\} $. This is a good thing.
\end{note}
\end{eg}

A group with this property is called \allbold{cyclic}.

\begin{defn}[generator]
	The elements 1 (or 3) for $\zz_4$ is called a \allbold{generator} for $\zz_4$. 
\end{defn}

\begin{defn}[cyclic group]
	A group is \allbold{cyclic} if it has a generator.
\end{defn}

\begin{defn}[generated subgroup]
The \allbold{subgroup generated by} $x \in G$ is the smallest subgroup of $G$ that contains $x$. We denote the subgroup generated by  $x$ by  $\langle x \rangle$. 
\end{defn}

\begin{eg}[]
In $V_4$, the following hold:
 \begin{itemize}
	\item $\langle a \rangle = \{e,a\} $ 
	\item $\langle b \rangle = \{e,b\} $ 
	\item $\langle c \rangle = \{e,c\} $ 
	\item $\langle e \rangle=\{e\} $
\end{itemize}
None of these is the whole group. This means $V_4$ is not cyclic, and has no generator.
\end{eg}

\begin{eg}[]
In $\zz_4$, 
\begin{itemize}
	\item $\langle 0 \rangle=\{0\} $ 
	\item $\langle 1 \rangle = \{0,1,2,3\} $ 
	\item $\langle 2 \rangle= \{0,2\} $ 
	\item $\langle 3 \rangle= \{0,1,2,3\} $
\end{itemize}
$\zz_4$ is cyclic, it is generated by 1 or 3.
\end{eg}
\end{document}
