\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\section{Group}
\begin{defn}[group]
	A \allbold{group} is a binary structure $(G,*)$ s.t. 
	\begin{enumerate}[label=\arabic*)]
		\item $(G,*)$ is associative
		\item (G,*) has an identity: there exists  $e \in G$ s.t.
			\[
			e*g=g*e=g \quad \forall g \in G
			.\] 
		\item $(G,*)$ has two-sided inverses for all $x \in G$, there exists a $y \in G$ s.t. \[
		x*y=y*x=e
		.\] 
	\end{enumerate}
\end{defn}

\begin{eg}[]
	$(\zz,+)$ is a group. 
\end{eg}

\begin{defn}[abelian group]
A group in which $*$ is commutative is called  \allbold{abelian}. 
\end{defn}

\begin{eg}[]
\begin{itemize}
	\item $\zz^+$ under $+$: has no identity.
	\item $N_0$ under  $+$:  $1$ doesn't have an inverse.
	\item  $(\qq^* , \times)$ nonzero rationals under $\times $: yes
	\item $(\qq,\times )$: $0$ doesn't have an inverse.
	\item  $(\zz^{\times },\times )$ nonzero integers under $\times $: 2 doesn't have an inverse.
	\item $(\zz_n,+_{n} )$ integers mod n under addition mod n is a group. Associativity is not obvious yet.
	\item $(\zz_7^*,\times_7  )$ is a group.
	\item $(M_n(\rr),+)$ $n\times n$ matrices with real entries under matrix addition: is a group.
	\item $(M_n(\rr),\times )$ under matrix multiplication. The zero matrix have no inverse.
	\item $(GL_n(\rr),\times )$ the invertible $n\times n$ matrices in the general linear group under $\times $.
	\item $GL_2(\rr)$ is nonabelian. 
		\begin{align*}
			\begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix} \begin{pmatrix} 1&0\\1&1 \end{pmatrix} &= \begin{pmatrix} 2&1\\1&1 \end{pmatrix}  \\
			\begin{pmatrix} 1&0\\1&1 \end{pmatrix} \begin{pmatrix} 1&1\\0&1 \end{pmatrix}  	&= \begin{pmatrix} 1&1\\1&2 \end{pmatrix}  
		\end{align*}
\end{itemize}

\end{eg}
\begin{thm}[]
	Let $(G,*)$ be a group. 
	\begin{itemize}
		\item If  $a*b=a*c$, then  $b=c$. 
		\item If $b*a=c*a$, then  $b=c$.
	\end{itemize}
\end{thm}

\begin{prf}
	Suppose $a*b=b*c$, then
	\begin{align*}
		a^{-1}*(a*b) &=a^{-1} * (a*c)\\
		(a^{-1}*a)*b &= (a^{-1}*a)*c \\
		e*b&= e* c \\
		b&=c
	\end{align*}
\end{prf}

\begin{eg}[group with 3 elements]
	$(\zz_3,+_3)$.

	G=\{e,a,b\}.
\begin{table}[htpb]
	\centering
	\begin{tabular}{c||c|c|c}
		*&e&a&b\\
		\hline
		e&e&a&b\\
		\hline
		a&a&b&e\\
		\hline
		b&b&e&a\\
	\end{tabular}
\end{table}

\begin{remark}
	Any group with 3 elements is isomorphic to $(\rr_3,+_3)$.
\end{remark}
\end{eg}
\begin{eg}[groups of order 2]
\begin{table}[htpb]
	\centering
	\begin{tabular}{c||c|c}
		*&e&a\\
		\hline
		e&e&a\\
		\hline
		a&a&e
	\end{tabular}
\end{table}
\end{eg}

\begin{eg}[groups of order 4]
See iPad.
\end{eg}

\begin{eg}[]
	$(U,\times )$ (all complex numbers that form unit circle) and $(U_n,\times )$ are groups.
\end{eg}
\end{document}
