\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\begin{thm}[Kolmogoro's 0-1 Theorem]
	Suppose $ A_1,\ldots$ are independent events. For any $ A$ in the generated tail  $\sigma$-field, we have either $ P(A) =0$ or  $ P(A)=1$.
\end{thm}
\section{Simple Random Variables}
\begin{defn}[simple random variable]
Let $ (\Omega,\mathcal{F},P)$ be a probability space. A function $ X:\Omega \to \rr$ is a \allbold{simple random variable} if 
	\begin{enumerate}[label=(\roman*)]
		\item it assumes finitely many values (finite range).
		\item For any $ x \in \rr$, 
			\[
				\{X=x\}\coloneqq \{\omega: X(\omega)=x\} \in \mathcal{F}  
			.\]
			"The inverse image of $ x$ under  $ X$ is in  $ \mathcal{F}$". We say that "$ X$ is measurable wrt  $ \mathcal{F}$", or $ X$ is $ \mathcal{F}$-measurable.
	\end{enumerate}
\end{defn}

\begin{defn}[indicator random variables]
	Let $ A$ be a set. The \allbold{indicator random variable}
\begin{equation*}
	I_A(\omega)=
\begin{cases}
	1 &\text{ if } \omega \in A\\
	0 & \text{ if } \omega \not\in A 
\end{cases}
\end{equation*}
\end{defn}

\begin{thm}
Suppose $ A_1,A_2,\ldots,A_n \in \mathcal{F}$ form a finite partition of $ \Omega$. Define
\[
	X(\omega)=\sum_{ i= 1}^{ n} a_i I_{A_i} (\omega)
.\] 
for some fixed $ a_1,\ldots,a_n \in \rr$. Then $ X$ is a simple r.v.
\end{thm}
\begin{note}[]
Every simple r.v. can be written in this way.
\end{note}

\begin{thm}[]
	An indicator r.v. $ X(\omega) = I_A(\omega)$ is measurable wrt $ \mathcal{F} \implies A \in \mathcal{F}$.
\end{thm}

\begin{defn}[]
	$ (\Omega,\mathcal{F},P)$, $ X$ a simple r.v. on  $ (\Omega,\mathcal{F},P)$. Let $ \mathcal{ G} \subseteq \mathcal{F}$ be another $\sigma$-field. We say that \allbold{$ X$ is measurable wrt  $ \mathcal{ G}$} if for any $ x \in \rr$, $ \{w:X(\omega)=x\} \in \mathcal{ G} $ .
\end{defn}

\begin{note}[]
$ \mathcal{ G} \subseteq \mathcal{F}$. If $ X$ is measurable wrt  $ \mathcal{ G}$. Then for any $ H \subseteq \rr$,
\[
	\{\omega:X(\omega) \in H\} = \bigcup_{x \in H} \{\omega: X(\omega) = x\} \in \mathcal{ G}
.\] 
which might be an uncountable union unless $ X$ is simple so it has finite range.
\end{note}

\begin{defn}[the sigma-field generated by $ X$]
	The \allbold{ $\sigma$-field generated by $ X$}, denoted $ \sigma(X)$, is the smallest $\sigma$-field wrt which $ X$ is measurable. 
\end{defn}
\begin{note}[]
It is the intersection of a $\sigma$-field wrt which $ X$ is measurable.
\end{note}

\begin{defn}[sigma-field generated by a sequence of r.v.]
	For a finite or infinite sequence $ X_1,X_2,\ldots$ of simple r.v., $\sigma(X_1,X_2,\ldots)$ is the smallest $\sigma$-field wrt which each $ X_i$ is measurable.
\end{defn}
\begin{thm}[5.1]
	Let $ X_1,\ldots,X_n$ be a finite sequence of simple r.v.s.
	\begin{enumerate}[label=(\roman*)]
		\item The $\sigma$-field, $ \sigma(X_1,\ldots,X_n)$, consists of all subsets of $ \Omega$ of the form 
			\[
				\{\omega:(X_1(\omega),\ldots,X_n(\omega)) \in H\} \text{ for any } H \subseteq \rr^{n} 
			.\] 
		\item A simple r.v. $ Y$ is measurable wrt  $ \sigma(X_1,\ldots,X_n)$ if and only if $ Y=f(X_1,\ldots,X_n)$ for some $ f: \rr^{n} \to \rr$.
	\end{enumerate}
\end{thm}
\end{document}
