\documentclass[class=article,crop=false]{standalone} 
\input{../preamble.tex}

\begin{document}
\begin{defn}[density]
A r.v. $ X$ and the corresponding distribution  $ P_X$ has a  \allbold{density} $ f$ wrt Lebesgue measure if 
 \begin{enumerate}[label=(\roman*)]
	 \item $ f: \rr \to [0,\infty]$ is measurable $ \mathcal{B}(\rr) / \mathcal{B}(\rr^{+} \cup \{+ \infty\}) $.
	 \item For all $ A \in \mathcal{B}(\rr)$,
		 \[
			 P_X(A) = P(X \in A) = \int_A f(x) dx
		 .\] 
\end{enumerate}
\end{defn}

\begin{note}[]
~\begin{enumerate}[label=\arabic*)]
	\item can define wrt other measures.
	\item we have the familiar
		\[
			\int_{\rr} f dx = P_X (\rr) = p(X \in \rr) = P(\Omega) = 1
		.\]
	\item A r.v. $ X$ may have multiple densities wrt Lebesgue measure. They can only differ on sets with Lebesgue measure zero.
\end{enumerate}
\end{note}

\begin{claim}
Define $ F(x) = P(X\leq x) = P(X \in (-\infty,x]) = \int_{-\infty}^x f(t) dt$. If $ F$ is a cdf (right-continuous, etc), then this equation implies that  $ F$ is continuous. 
\end{claim}

Consider the random vector $ X = (X_1,\ldots,X_k)$. 
\begin{enumerate}[label=\arabic*)]
	\item This induces a probability measure $ P_X(A) = P((X_1, \ldots, X_k) \in A) \ \forall \ A \in \mathcal{B}(\rr^{k})$. 
	\item has a distribution function
		\[
			F_X(x_1,\ldots,x_k) \coloneqq P(X_1 \leq x_1, \ldots, X_k \leq x_k)
		.\]
	\item may or may not have a density $ f$ satisfying  $ P_X(A) = \int_A f(t) dt$.
		 \begin{align*}
			 F_X(x_1,\ldots,x_k) = \int_{-\infty}^{x_k} \ldots \int_{-\infty}^{x_1} f(t_1,\ldots,t_k) dt_1 \ldots dt_k
		\end{align*}
\end{enumerate}

\begin{property}
~\begin{enumerate}[label=\arabic*)]
	\item non-decreasing on each variable (intersections).
	\item right-continuous in each variable. That is,
		\[
			\lim_{ x_i \searrow a} F_X(x_1,\ldots,x_k) = F(x_1,\ldots,x_{i-1},a,x_{i+1},\ldots,x_k).
		.\] 
		When $ k=2$, this is often referred to as "continuity from the right and from above".
	\item $ \lim_{ x_i \to -\infty} F_X(x_1,\ldots,x_k) =0$.
	\item $ \lim_{ x_i \to \infty} F_X(x_1,\ldots,x_k) = F_X(x_1,\ldots,x_{i-1},x_{i+1},\ldots,x_k)$. This is the marginal CDF. Taking all $ x_i \to \infty$ gives us 1.
	\item $ F_X$ can have an uncountable number of discontinuities.
		 \begin{eg}[]
			 In $ \rr^2$, Extend Lebesgue measure on $ [0,1]$ to  $ \rr^2$ as follows:

			 Let $ A \in \mathcal{B}(\rr^2)$, $ X=(X_1,X_2)$. Define
			 \[
				 P_X(A) = \lambda(A \cap \{(x,y): 0\leq x \leq 1, y=0\} )
			 .\] 
			 It's the length of the overlap of $ A$ with $ [0,1]$. Note that $ P_X$ is a probability measure on  $ \rr^2$ because it is between 0 and 1, $ P_X( \O) =0$, and $ P_X(\rr^2)=\lambda([0,1])=1$. And given $ A_1,\ldots$ disjoint, then
			  \begin{align*}
				  P_X\left( \bigcup_{ n =1}^{\infty} A_n \right) &= \lambda \left( \left( \bigcup_{ n =1}^{\infty} A_n \right) \cap [0,1]  \right)  \\
										 &= \lambda\left( \bigcup_{ n =1}^{\infty} (A_n \cap [0,1]) \right)  \\
										 &= \sum_{ n= 1}^{\infty} \lambda(A_n \cap [0,1]) \text{ disjoint} \\
										 &= \sum_{ n= 1}^{\infty} P_X(A_n) \\
			  \end{align*}
			  Now define $ F(x_1,x_2) = P(X_1\leq x_1, X_2\leq x_2)$. Then
			   \begin{align*}
				   F(1,0) &= P(X_1\leq 1, X_2 \leq 0) \\
					  &= P_X((-\infty,1] \times (-\infty,0]) \\
					  &= \lambda ([0,1]) =1
			  \end{align*}
			  Notice
			  \[
				  F(1,0^-)= P(X_1\leq 1, X_2 < 0) = 0
			  .\] 
			  which is a jumped discontinuity. In fact, $ F(a,0)$ and  $ F(a,0^-)$ for any  $ a \in[0,1]$ will give us a jump discontinuity. And this is uncountably many of $ a$. 
		\end{eg}

	\item In general, since cdfs are right-continuous,  $ F$ is continuous at  $ x \implies F$ is right continuous at  $ x \implies$ the boundary of the half rectangle $ \{y:y_i\leq x_i, i=1,2,\ldots,k\} $ has probability measure zero. 
	\item OTOH, while $ F$ may have an uncountably infinite number of discontinuities, the points of continuities are a dense set in  $ \rr^{k}$.
		\begin{prf}
			Sketch: Take any $ x \in \rr^{k}$ and consider the half rectangles $ \{y_i: y_i\leq x_i + h, i=1,\ldots,k\} $ for various $ h$. The boundaries of these half rectangles are disjoint. Recall from Section 10 if a measure  $ \mu$ on a $\sigma$-field $ \mathcal{F}$ is $\sigma$-finite, then $ \mathcal{F}$ cannot contain an uncountable disjoint collection of sets with positive $ \mu$ measure. $ P_X$ is finite  $ \implies P_X$ is $\sigma$-finite, so only countably many of the $ x+h$ rectangle boundaries can have positive  $ P_X$ measure. That is, only countably many of the  $ x+h$'s can be points of discontinuities for  $ F$. Therefore, we can always select points of continuity of  $ F$ that approach  $ x$ since $ h$ is arbitrary.
		\end{prf}
\end{enumerate}
\end{property}
\end{document}
