\documentclass[class=article, crop=false]{standalone} 
\input{../preamble.tex}
\begin{document}
\section{Probability Measures}
Let $\Omega$ be a non-empty set. 
(Think of it as a sample space = set of all possible outcomes of an experiment involving randomness.)
Ex: Flip a coin twice.
\[
	\Omega=\{HH,HT,TH,TT\}
.\]

Let $ A \subset \Omega$. 
Ex: $A=$ an event, $\{HT,TH,TT\}$.
With fair coin $P_r (A) = \frac{3}{4}$

To measure a 2D blob: usual length, area, volume ..

We want to assign probability to subsets of $\Omega$\\
$P:$ subsets of  $\Omega \to [0,1]$.

\begin{defn}[field]
	Let $\Omega$ be a non-empty set. Let $\mathcal{F}$ a collection of subsets of $\Omega$. $\mathcal{F}$ is called a \allbold{field (or algebra)} if
	\begin{enumerate}
		\item $\Omega \in \mathcal{F}$
		\item $A\in \mathcal{F} \implies A^{c} \in \mathcal{F} $ ("closed under complements")
		\item Given $A_1,A_2,\ldots \in \mathcal{F} \implies \bigcup_{i= 1}^{ n} A_i \in \mathcal{F}$ ("closed under finite unions"). 
	\end{enumerate}
\end{defn}
\begin{remark}
We can also use "closed under intersection" to define because of De Morgan's law.
\end{remark}
\[
	\left( \bigcap_{i= 1}^{ n} A_i \right)^{c} = \bigcup_{i= 1}^{ n} A_i^{c}
.\] 
\begin{defn}[sigma-field]
	If (iii) is replaced by a \emph{countable} union, e.g. $\bigcup_{n= 1}^{\infty} A_n $, then $\mathcal{F}$ is called a \allbold{$\sigma$-field}.  
\end{defn}
\begin{remark}
$\sigma$ field is stronger than field.
\end{remark}
\begin{eg}[sigma-fields]
TODO
\end{eg}
$\Omega$.\\

\begin{itemize}
	\item $\mathcal{F}=\{\O,\Omega\}$
	\item $\mathcal{F} =$ the power sets (all possible subsets of $\Omega$). (Billingsley:"power class").
	\item Take any $A\subset \Omega$. Define $\mathcal{F}=\{\O,A,A^{c},\Omega\}$
\end{itemize}

A counterexample of a field that is not a $\sigma$-field.
Let $\Omega = \rr$, $\mathcal{F}=$ the empty set and all finite disjoint unions of things like $(a,b]$ and/or  $(a,\infty)$ for $-\infty\leq a<b<\infty$.\\
(i) $\Omega=(-\infty,\infty) \in \mathcal{F}$.\\
(ii) Complements: Ex: $(a,b]^{c} =(-\infty,a] \cup (b,\infty)$. More generally a set in $\mathcal{F}$ has the form a bunch of disjointed $(]$ or $(\infty)$. \\
(iii)\\ 
\begin{case}[1]
$A_1,A_2$ have no overlaps. Then $A_1 \cup A_2$ is still a finite disjointed union.
\end{case}
Case 2: Some overlap, then $A_1 \cup A_2$ is still the same type of interval.\\
However, it is not a $\sigma$-field. We want to find a countable collection of sets that isn't in here. Let $A_n=(0,1-\frac{1}{n}]$. Then $\bigcup_{n= 1}^{ \infty} A_n =(0,1) \not \in \mathcal{F} $.
\begin{defn}[generated sigma-field]
	Let $\mathcal{A}$ be a collection of subsets of $\Omega$. The \allbold{ $\sigma$-field generated by $\mathcal{A}$} is the smallest $\sigma$-field containing all the sets in $\mathcal{A}$. We write it as $\sigma(\mathcal{A})$.
\end{defn}
i.e. Any $\sigma$-field containing $\mathcal{A}$  must contain $\sigma(\mathcal{A})$.
Note: 
\begin{itemize}
	\item If $\mathcal{F}$ is a $\sigma$-field, $\sigma(\mathcal{F})=\mathcal{F}$.
	\item If $\mathcal{F}$ is a $\sigma$-field and $\mathcal{A}\subset \mathcal{F}$, then $\sigma(\mathcal{A}) \subset \mathcal{F}$.
	\item $\sigma(\mathcal{A}) = \bigcap \mathcal{F}$ the intersection over all $\sigma$-field that contain $\mathcal{A}$.
	\item $\mathcal{A}\subset \mathcal{A}' \implies  \sigma(\mathcal{A}) \subset \sigma(\mathcal{A}')$ 
\end{itemize}

Example:
\begin{itemize}
	\item $A \subset \Omega, \mathcal{A}=\{A\} \implies \sigma(\mathcal{A})=\sigma(A)=\{\O,A,A^{c},\Omega\}$
	\item \allbold{Borel Sets} in $\rr$. Let $\Omega=\rr$, $\mathcal{A}=$ all open finite intervals in $\rr$. $\mathcal{B}(\rr)=\sigma(\mathcal{A})$. Note: include all half open intervals. It also contains single points: $\{a\}=\bigcap_{n= 1}^{ \infty} (a,a+\frac{1}{n}]$. Cantor sets are not in here. 
\end{itemize}
\subsection{Unions and Intersections of sigma-fields}.
\begin{itemize}
	\item The union of two $\sigma$-Fields is not a necessarily a $\sigma$-Field. Take $A,B \subset \Omega, A \neq B, \sigma(A)=\{\O,A,A^{c},\Omega\}, \sigma(B)={\O,B,B^{c},\Omega}$. So 
			$\sigma(A) \cup \sigma(B)$ 
		\item The intersection (including uncountable intersection) of two $\sigma$-Fields is a $\sigma$-Field. Let $\mathcal{F}_1,\mathcal{F}_2$ be two $\sigma$-Fields. $\mathcal{F}_1 \cap \mathcal{F}_2$ 
			(i) $\Omega \in \mathcal{F}_1 \cap \mathcal{F}_2$ since $\O \in \mathcal{F}_1$ and $\O \in  \mathcal{F}_2$.
			(ii) Let $A \in \mathcal{F}_1 \cap \mathcal{F}_2$ 
			$A \in \bigcap_{n= 1}^{ \infty} \mathcal{F}_n \implies A \in \mathcal{F}_n \forall n \implies A^{c} \in \mathcal{F}_n \forall n \implies A^{c} \in \bigcap_{n= 1}^{ \infty} \mathcal{F}_n $
\end{itemize}
\end{document}
